### 2012-10-02 docs/FAQ/faq.tex
add Warren's question

@@

>>>>

\item {\em Why is everything in its own module?}

   If a subroutine is in a Fortran module, then at compile time, 
   there is argument checking.  This ensures that the right number
   and data types of arguments are present.  It makes the code safer.

@@

\item {\em Why did we switch all the equations over to the
  $\tilde{\Ub}$ form instead of just working with $\Ub$?}

This is basically a numerical discretization issue.  Whenever the base
state aligns with the grid, you should be able to show that you get
exactly the same answer each way.

When you do a spherical star on a 3d Cartesian grid, though, the $w_0$
is defined on the radial mesh and the $\tilde{\Ub}$ on the Cartesian
mesh, and the $w_0$ part never experiences the Cartesian projection,
for example.  So there are differences in exactly how the $w_0$ component
appears (projected on the Cartesian mesh vs.\ interpolated from the
radial mesh)---we made the decision at the time to separate the
components for that reason.
